\mychapter{charms}{Charms}

\CharmSection{dodge-charms}{Dodge Charms}

\begin{Charm}{Threshold Warding Stance}{%
    Cost=2m~per~+1~Evasion \emph{or} success,
    Mins={Dodge 1, Essence 1},
    Type=Supplemental \emph{or} Reflexive,
    Keywords={Balanced, Excellency, Fire, Uniform},
    Duration=Instant,
    Reference=\cite*[p.~190]{db}
}{threshold-warding-stance}
    The Dragon-Blood's body is as light as flames, skimming over the ground as
    she moves to evade. \tldr{She may raise her Evasion for two motes per
    point, or add automatic successes on a Dodge roll for two motes each. She
    ignores environmental penalties to her Evasion or the Dodge roll.}
\end{Charm}



\CharmSection{integrity-charms}{Integrity Charms}

\begin{Charm}{Granite Curtain of Serenity}{%
    Cost=2m~per~+1~Resolve \emph{or} success,
    Mins={Integrity 1, Essence 1},
    Type=Supplemental \emph{or} Reflexive,
    Keywords={Balanced, Earth, Excellency},
    Duration=Instant,
    Reference=\cite*[p.~194]{db}
}{granite-curtain-of-serenity}
    Taking on the stoicism of stone, the Dragon-Blood stands unmoved by honeyed
    words or ferocious threats. \tldr{She may raise her Resolve or add
    automatic successes to an Integrity roll for two motes each. In addition,
    she ignores a single point of penalty from wounds, deprivation, or poison.}
\end{Charm}



\CharmSection{linguistics-charms}{Linguistics Charms}

\begin{Charm}{Cryptic Essence Cipher}{%
    Cost=5m,
    Mins={Linguistics 2, Essence 1},
    Type=Simple,
    Keywords={Water, Written-only},
    Duration=Instant,
    Reference=\cite*[p.~209]{db}
}{cryptic-essence-cipher}
    The Dragon-Blood's mastery of speech and language is synonymous with her
    mastery of deception. \tldr{She rolls \Pool{\Options*{\StatVal{Manipulation},
    \StatVal{Intelligence}} + \StatVal{Linguistics}} to create a coded message,
    designating a single character who can understand it.} Through her insight
    into his mind, she devises a cipher that he can intuitively read --- for
    him, the symbols on the page seem to rearrange themselves to spell out the
    hidden message. \tldr{For others, deciphering the message, even with
    code-breaking magic, requires a \Pool{\Options*{\Val{Perception},
    \Val{Intelligence}} + \Val{Linguistics}} roll opposing the Dragon-Blood's
    initial roll.}

    Alternatively, the Dragon-Blood may draw from one of her Principles to
    create a code that can be intuitively understood by any character who
    shares that Intimacy.
\end{Charm}



\CharmSection{lore-charms}{Lore Charms}

\begin{Charm}{Careful Insight-Gathering Study}{%
    Cost=2m per success,
    Mins={Lore 1, Essence 1},
    Type=Supplemental,
    Keywords={Air, Balanced, Excellency},
    Duration=Supplemental,
    Reference=\cite*[p.~214]{db}
}{careful-insight-gathering-study}
    Breating deep of the world's Essence, the Dragon-Blood pronounces her
    wisdom with impeccable clarity. \tldr{She may add automatic successes to a
    Lore roll for two motes each. In addition, if she adds 2+ successes on a
    roll to introduce or challenge a fact~\parencite*[pp.237-238]{ex3}, she
    doubles 9s on the roll.}
\end{Charm}


\begin{Charm}{Opening the Mind's Gates}{%
    Cost=3m,
    Mins={Lore 2, Essence 1},
    Type=Simple,
    Keywords=Air,
    Duration=Instant,
    Reference=\cite*[p~214]{db}
}{opening-the-minds-gates}
    Speaking a sagely aphorism, the Dragon-Blood calls up the winds of
    knowledge to dispere whatever miasma closes a student's mind to learning.
    \tldr{She makes a special instill roll with
    \Pool{\Options*{\StatVal{Charisma}, \StatVal{Intelligence}} + \StatVal{Lore}}
    to induce a state of supernatural receptivity in a single character},
    treating him as though he had a Major Principle of ``I must seek out
    education'' for one scene. \tldr{If the Dragon-Blood exploits this Intimacy
    with a persuade or bargain roll to convince the target to study with her,
    the cost of resisting increases by one Willpower.}
\end{Charm}


\begin{Charm}{Elemental Concentration Trance}{%
    Cost=3m,
    Mins={Lore 3, Essence 1},
    Type=Simple,
    Keywords=Balanced,
    Duration=Instant,
    Reference=\cite*[p.~214]{db}
}{elemental-concentration-trance}
    To use this Charm, the Dragon-Blood must spend a few minutes contemplating
    an expression of an element; observing the movement of clouds, meditating
    beneath a waterfall, staring unblinkingly into a flame, or so on; this
    determines the Charm's elemental aspect. \tldr{At the end, she makes a
    \Pool{\Val*{Mental Attribute} + \Options*{\StatVal{Bureaucracy},
    \StatVal{Investigation}, \StatVal{Lore}, \StatVal{Medicine},
    \StatVal{Survival}, \StatVal{War}}} roll with a single bonus success.
    She may roll to introduce a fact as though she has a Lore background in
    facts that relate to the Charm's elemental aspect.} An Air-aspected use
    could introduce facts about weather or music theory; an Earth-aspected use
    could relate to geology, masonry, or architecture; and so on.

    \begin{Unavailable}
        If the Dragon-Blood knows Dragon-Kin Empowerment, she may provide the
        benefits of this Charm to one of her Sworn Kin, guiding him through
        meditation.
    \end{Unavailable}
\end{Charm}



\CharmSection{occult-charms}{Occult Charms}


\begin{Charm}{Hidden Secrets Whispers}{%
    Cost=1m per die,
    Mins={Occult 1, Essence 1},
    Type=Supplemental,
    Keywords={Air, Balanced, Excellency},
    Duration=Instant,
    Reference=\cite*[p.~230]{db}
}{hidden-secrets-whispers}
    Attuned to the subtle winds of the spiritual, the Dragon-Blood draws forth
    sublime truths. \tldr{She may add bonus dice to an Occult roll for one mote
    each. Each 10 rerolls a non-1 failed die.}
\end{Charm}


\begin{Charm}{Seed and Salt Warding}{%
    Cost={1m, 1wp},
    Mins={Occult 3, Essence 1},
    Type=Simple,
    Keywords={Earth \emph{or} Wood},
    Duration=One day,
    Reference=\cite*[p.~230]{db}
}{seed-and-salt-warding}
    The Dragon-Blood lays down a line of salt or germinated grain to keep
    ghosts at bay~\parencite*[p.506]{ex3}, spanning up to a single range band.
    The aspect of this Charm depends on which she uses --- salt is Earth, while
    grain is Wood. \tldr{She rolls \Pool{\StatVal{Intelligence} +
    \StatVal{Occult}} to determine the power of the warding. Powerful ghosts
    who could normally cross the line by spending Willpower can only do so if
    their Resolve exceeds the Dragon-Blood's successes on her Occult roll.}
    Otherwise they cannot cross the line. The line lso repels other forms of
    undead, such as zombies or hungry ghosts.
\end{Charm}


\begin{Charm}{Spirit-Detecting Mirror Technique}{%
    Cost=4m,
    Mins={Occult 1, Essence 1},
    Type=Reflexive,
    Keywords={Air, Balanced},
    Duration=One scene,
    Reference=\cite*[p.~230]{db}
}{spirit-detecting-mirror-technique}
    Drawing back the veil between worlds, the Dragon-Blood makes invisible
    spirits and phantasms visible within the glass. To use this Charm, she must
    be touching a mirror or a similar reflective surface, such as the blade of
    a well-polished daiklave. The Exalt can see the reflections of
    dematerialized characters in that mirror, and can even hear what they say
    in the form of whispers that rise up from the mirror's surface. Only the
    Exalt is capable of seeing the reflection --- th others, even the spirit
    itself, it doesn't appear in the mirror.

    This doesn't allow the Dragon-Blood to physically interact with spirits,
    but it can be used in conjunction with magic that does. Using reflections
    to pinpoint a foe is somewhat awkward --- instead of fully negating the
    \Modifier{-3} penalty for attacking a dematerialized spirit one can't see,
    it reduces the penalty to \Modifier{-1}.

    \begin{Unavailable}
        An Occult 5, Essence 3 repurchase of thie Charm lets the Dragon-Blood
        pay one Willpower to make the spirit reflections visible and audible to
        her allies as well. Their attacks against it still take a \Modifier{-1}
        penalty.
    \end{Unavailable}
\end{Charm}


\begin{Charm}{Secret Wind Revelation}{%
    Cost=3m,
    Mins={Occult 3, Essence 1},
    Type=Reflexive,
    Keywords={Air, Balanced},
    Duration=Instant,
    Prerequisites=\nameref{charm:spirit-detecting-mirror-technique},
    Reference=\cite*[p.~231]{db}
}{secret-wind-revelation}
    Attuned to subtle currents of spiritual wind, the Dragon-Blood can hear a
    demon's whispers or a ghost's tread. \tldr{When a dematerialized entity
    comes within long range or closer of the Exalt, the Storyteller informs her
    player that she may activate this Charm. She rolls
    \Pool{\StatVal{Perception} + \StatVal{Awareness}} with
    \Pool{\StatVal{Occult}} bonus dice opposing its \Pool{\Val{Dexterity} +
    \Val{Stealth}} roll to pinpoint its location.}

    A failed roll still reveals the presence of a dematerialized being nearby.
    However, that entity uses the result of its Stealth roll to establish
    concealment against the Dragon-Blood until the scene ends or it breaks
    concealment, escaping her notice even if she later uess
    \nameref{charm:spirit-detecting-mirror-technique}. She cannot use this
    Charm against the same spirit for the rest of the scene.
\end{Charm}



\CharmSection{sorcery-charms}{Sorcery Charms}

\begin{Charm}{Terrestrial Circle Sorcery}{%
    Mins={Occult 3, Essence 1},
    Type=Permanent,
    Duration=Permanent,
    Prerequisites=Any four Occult Charms,
    Reference=\cite*[p.~235]{db}
}{terrestrial-circle-sorcery}
    The Dragon-Blood steps across the threshold of the Emerald Circle, and is
    forever changed. She gains the ability to cast spells of the Terrestrial
    Circle, and learns one shaping ritual~\parencite*[p.~466]{ex3} and one
    Terrestrial Circle spell, which becomes her control spell.
\end{Charm}



\CharmSection{thrown-charms}{Thrown Charms}

\begin{Charm}{Seeking Throw Technique}{%
    Cost=1m per die,
    Mins={Thrown 1, Essence 1},
    Type=Supplemental,
    Keywords={Air, Balanced, Excellency, Uniform},
    Duration=Instant,
    Reference=\cite*[p.~275]{db}
}{seeking-throw-technique}
    The Dragon-Blood's hostile intent stirs up a current of wind that guides
    her weapon to its victim. A thrown knife might change tragectory midair to
    strike an enemy hidden behind a tree, wall, or similar cover. \tldr{She may
    add bonus dice on a Thrown roll for one mote each, and ignores the Defense
    bonus of enemies in light cover.}

    \tldr{In Air Aura, if the Dragon-Blood aims before attacking, she may
    ignore one point of Defense bonus from heavy cover.}
\end{Charm}


\printbibliography[title=References]

