\mychapter{spells}{Spells}


\CharmSection{terrestrial-circle-spells}{Terrestrial Circle Spells}


\begin{Spell}{Beckoning That Which Stirs the Sky}{%
    Cost={Ritual, 2wp},
    Duration={\Pool{1 + \Val{threshold }\allowbreak\Val{successes}}~hours},
    Reference=\cite*[p.~309]{db}
}{beckoning-that-which-stirs-the-sky}
    As the sorcerer recites ancient prayers to deities long forgotten beneath
    the open sky, huge chitinous limbs emerge from above, weaving the wind and
    clouds to her will. \tldr{Shaping the weather is an
    \Pool{\StatVal{Intelligence} + \StatVal{Occult}} roll that takes a few
    minutes to complete, with a difficulty based both on how drastic the change
    the sorcerer wishes to make is and how typical the desired weather is for
    her current climate and season.} Creating a light rain in a temperate
    climate might only be difficulty 1, while strengthening a heavy rin to a
    thunderstorm or halting it completely might be difficulty 2-3. Summoning a
    thunderstorm from blue skies or diminishing a hurricane to a severe storm
    would be difficulty 5+. Likewise, any attempt to create rain might incur
    increased difficulty if attempted in a desert, as would calling a blizzard
    outside of the winter season. This spell can never create extreme natural
    disasters such as hurricanes, though it can diminish them to a lesser
    weather.

    If the sorcerer succeeds, That Which Stirs the Sky weaves the desired
    weather in an area out to \Pool{\StatVal{Essence} + \Val{threshold
    successes}} miles from the point she cast the spell. It lasts for \Pool{1 +
    \Val{threshold successes}} hours before reverting to normal. Subsequent
    castings by any sorcerer cannot alter the weather within the spell's rnge
    until its duration elapses. \tldr{Characters within the weather can
    identify its unnatural origin with a \Pool{\Val{Perception} +
    \Options{\Val{Occult}, \Val{Survival}}} roll of difficulty 1--5, with
    subtler alterations being more difficult to detect.}

    \begin{Unavailable}
        A sorcerer with this as her control spell may create sorcerous weather
        that follows her as she moves; this costs half her threshold successes,
        rounded up.
    \end{Unavailable}

    \textit{Distortion} (Goal Number:~10): Distorting this spell reverses the
    alteration to the weather. It doesn't merely revert back to its previous
    conditions, but is changed in the other direction --- if the original
    sorcerer had calmed a thunderstorm, distortion would result in an even
    greater storm; if she'd summoned rain, distortion could result in intensely
    arid heat.
\end{Spell}


\begin{Spell}{Cirrus Skiff}{%
    Cost={15sm, 1wp},
    Duration=Until ended,
    Reference=\cite*[p.471]{ex3}
}{cirrus-skiff}
    The sorcerer calls down a Cirrus Skiff to bear her skyward, a small white
    puffy cloud just large enough for her and one other passenger to ride upon.
    The cloud descends from the sky and hovers near the sorcerer like a
    faithful puppy until she steps on, at which point it rises into the air,
    obeying her mental commands. It is slow-moving, managing a pace of only
    \Pool{\StatVal{Essence} \times 6} miles per hour, but it is virtually
    unlimitted in its flight capability, able to rise upward with no limit
    other than the ability of its caster to endure the rarified air of the
    upper atmosphere. \tldr{In combat, the sorcerer rolls
    \Pool{\StatVal{Wits} + \StatVal{Occult}} in place of standard movement
    rolls to mentally direct the cloud, but otherwise faces no complications or
    penalties.}

    If the sorcerer wishes to sleep, study, or otherwise rest on the Cirrus
    Skiff without having to give it constant instructions, she may give it a
    set command, such as ``Fly a mile up into the air and stay there'' or
    ``Circle around the satrap's palace,'' which it will obey until she gives
    it new orders. The sorcerer may disembark from the skiff for up to one
    scene without ending the spell, but any absence beyond that ends the spell,
    sending the cloud flying back up into the stratosphere.

    A character who knows Cirrus Skiff as her control spell may cast it with an
    Indefinite duration. Her conjured cloud will follow after her after she
    disembarks, eagerly awaiting her return without ever leaving. It will
    follow simple instructions from the sorcerer, even when she's not riding
    it, and can be summoned by the sorcerer's call from anywhere in Creation,
    proceeding to her side at the best speed it can manage.

    \textit{Distortion} (Goal Number:~7): Distorting a Cirrus Skiff weighs
    it down, turning the cloud into a heavy, dense fog for a scene. The
    sorcerer suffers a \Modifier{-3} penalty on the Occult roll to control the
    skiff's movement, and it cannot fly above long range from the ground. If it
    is already higher than that, it begins dropping at a rate of two range
    bands per round, in addition to any other movement the sorcerer takes.
\end{Spell}


\begin{Spell}{Corrupted Words}{%
    Cost={15sm, 1wp},
    Keywords=Psyche,
    Duration=Indefinite,
    Reference=\cite*[p.~472]{ex3}
}{corrupted-words}
    The sorcerer speaks words that bind the tongue --- she evokes a seething,
    bilious mass of green Essence between her hands and casts it down the
    throat of a victim at short range, where it dissolves into a ward that
    censors that character's mind. As she does, she forbids the victim from
    speaking of a single subject, which may be as specific as ``The letters I
    secretly send to the All-Seeing-Eye at the end of every month'' or as broad
    as ``The existence of Sidereal Exalted.'' \tldr{It is impossible to defend
    against the curse barring magic that can perfectly dodge or parry
    uncountable damage such as Heavenly Guardian Defense, but the sorcerer
    must roll \Pool{\StatVal{Intelligence} + \StatVal{Occult}} against the
    victim's Resolve to successfully bind his will.}

    A cursed character feels waves of nausea if he even thinks about trying to
    communicate anything about the topic. If he tries to do so despite this
    warning, he becomes overwhelmed with wracking pain and begins vomiting up
    dozens of fat, white maggots, rendering that action or any other impossible
    for at least a turn. This applies to all forms of communication ---
    speaking, writing, telepathy, or any desperate signals the victim tries to
    use to circumvent the restriction of this curse --- and persists until the
    cursed character ceases trying to violate the ban. This spell may be ended
    by the sorcerer's death, or may be willingly released, as the sorcerer
    reaches a hand down the victim's mouth and recites the last word of this
    spell backwards to extract a slimy egg-sac full of squirming larvae that is
    the physical embodiment of this curse.

    \begin{Unavailable}
        A sorcerer who knows Corrupted Words as her control spell may cast it
        with no obvious display of magical intervention other than a faint
        flash of green in her eyes, leaving her victim uncertain as to the
        afflictions's source.
    \end{Unavailable}

    \textit{Distortion} (Goal Number:~15): Distorting this curse makes it
    possible for the victim to speak around the forbidden subject matter for
    five minutes. He must speak using circumlocutions, flowery metaphors, or
    cryptic symbolism to communicate the broad gist of the topic, and cannot go
    into any level of detail beyond the most superficial. This does not avert
    the inevitable tide of maggots, but gives the victim enough time to speak
    before he must disgorge them.
\end{Spell}


\begin{Spell}{Death of Obsidian Butterflies}{%
    Cost={15sm, 1wp},
    Keywords={Decisive-only, Perilous},
    Duration=Instant,
    Reference=\cite*[p.~472]{ex3}
}{death-of-obsidian-butterflies}
    Sculpting Essence into a volant black glass, the sorcerer unleashes a
    cascade of obsidian butterflies. \tldr{She rolls
    \Pool{\StatVal{Perception} + \StatVal{Occult}} as an undodgeable
    \Keyword{decisive} attack applied in a line against enemies out to medium
    range.} This line is wide enough to strike all opponents within the width
    of a single range band and reaches high enough to strike aerial enemies who
    are at short range to the ground (medium range enemies in the air can still
    be targeted by directing the butterflies to fly along an upward path,
    rather than a horizontal one). \tldr{Battle groups are especially
    vulnerable to being cut down by this spell, taking a \Modifier{-2} penalty
    to Defense against it.}

    \tldr{The attack deals raw damage equal to the sorcerer's
    \Pool{\StatVal{Essence} + \Val{extra successes}}, or
    \Pool{\StatVal{Essence} + \StatVal{Occult} + \Val{extra successes}} against
    a battle group. It does not reset the sorcerer to base Initiative.} Scenery
    made of wood, glass, or other fragile materials is generally destroyed.
    After this spell has been cast, the obsidian butterflies fall to the ground
    and shatter, creating terrain that may be hazerdous for barefooted
    characters to traverse --- \tldr{treat as an environmental hazard
    inflicting two dice of lethal damage, difficulty 2 to resist with a
    \Pool{\StatVal{Dexterity} + \StatVal{Athletics}}}, and if the character is
    barefoot, difficult terrain as well. Any character wearing armored boots
    can generally ignore the debris.

    \begin{Unavailable}
        A sorcerer who knows Death of Obsidian Butterflies as her control spell
        gains \Pool{\StatVal{Essence}} bonus dice to the spell's attack roll.
        When her emotions run hot, butterfly silhouettes rise from her shadow.
        When she is angry, her fingernails turn to sharp volcanic glass, making
        it possible to cut cloth or paper, rend wood or flesh and other similar
        stunts.
    \end{Unavailable}
\end{Spell}


\begin{Spell}{Demon of the First Circle}{%
    Cost={Ritual, 2wp},
    Duration=Instant,
    Reference=\cite*[p.~473]{ex3}
}{demon-of-the-first-circle}
    The sorcerer conjures one of the least monsters of the Demon Realm into
    Creation, breaking and binding it to her will. This spell requires a ritual
    that begins at sundown, and ends at the stroke of midnight. A faint green
    glow traes out a rift between Creation and Hell, and a First Circle Demon
    of the sorcerer's choice is drawn forth, howling with rage, fear, or
    sorrow.

    \tldr{Demons summoned by this spell must be bound with an
    \Pool{\StatVal{Intelligence} + \StatVal{Occult}} roll against their
    Resolve.} The sorcerer may choose to make the demon her personal slave for
    a year and a day, giving it a Defining Tie of loyalty to her that cannot be
    weakened or altered by any means and setting its Resolve to 0 against any
    influence roll she makes. Alternatively, she may assign it to complete a
    specific task --- ``Construct a tower using these plans,'' ``Murder
    Magistrate Yang,'' ``Dig a tunnel through this wall'' --- for as long as it
    takes to complete. Task-bound demons form a Defining Principle of ``I must
    complete my task,'' which is similarly impervious to tampering. On a failed
    binding roll, the sorcerer is unable to bind the demon, and must make a
    \Pool{\StatVal{Wits} + \StatVal{Occult}} roll against a difficulty of the
    demon's Willpower to banish it back to Hell. If she fails, then the demon
    is unleashed, unbound, into Creation --- and is most likely very angry at
    her.
\end{Spell}


\begin{Spell}{Flight of the Brilliant Raptor}{%
    Cost={15sm, 1wp},
    Keywords={Decisive-only, Perilous},
    Duration=Instant,
    Reference=\cite*[p.~473]{ex3}
}{flight-of-the-brillian-raptor}
    The sorcerer shapes flames of diamond and ruby into the form of a majestic
    bird of prey, evoking the elemental majesty of the garda birds. \tldr{The
    player rolls \Pool{\StatVal{Perception} + \StatVal{Occult}} as a
    \Keyword{decisive} attack against an enemy at up to long range}, then sends
    the raptor streaking forth to consume her foe in deadly flames. The
    brilliant raptor embodies the sorcerer's will, \tldr{with a base lethal
    damage equal to \Pool{\Val{her Initiative} + \Val{current temporary
    Willpower}}, and resets her to base Initiative on a successful attack. As
    long as the raptor deals 3+ levels of damage to its target, it ignites a
    bonfire~\parencite*[p.~230]{ex3} that engulfs him and all terrain within
    short range of him, and burns until the end of the scene.}

    \begin{Unavailable}
        A sorcerer who knows Flight of the Brilliant Raptor as her control
        spell may use it to attack a target one range band beyond long range by
        paying an extra 5sm when casting the spell.
    \end{Unavailable}
\end{Spell}


\begin{Spell}{Floral Ferry}{%
    Cost={20sm, 1wp},
    Duration=Until journey is completed,
    Reference=\cite*[p.~310]{db}
}{floral-ferry}
    Tossing a leaf, petal, or fruit into a body of water, the sorcerer beckons
    it with mudras of hte turning seasonsto grow into a small, seaworthy craft.
    This is a ship with the following traits~\parencite*[p.244]{ex3}:

    \begin{description}[noitemsep]
        \item[Speed:] Magically impelled \Modifier{+2}; current \Modifier{+1};
            oars \Modifier{+1}; empty cargo \Modifier{+1}
        \item[Maneuverability:] \Modifier{+3}
        \item[Hull:] \Modifier{-1}/\Modifier{-2}/\Modifier{-4}/Incapacitated
        \item[Cargo:] One tone. The ship can comfortably carry a half-dozen
            passengers.
    \end{description}

    \tldr{Upon casting this spell, the sorcerer names the destination she
    intends to sail to. If she has even approximate knowledge of its location,
    the Floral Ferry will sail itself as close as possible to that destination,
    using the sorcerer's \Pool{\StatVal{Essence} + \StatVal{Occult}} for
    sailing rolls.} However, it lacks the sapience to engage in pursuit or
    naval combat. Other characters can attempt to sail it, although the Speed
    bonus from its magically impelled travel becomes a \Modifier{-1} penalty if
    they attempt to travel anywhere but the named destination. Once it's
    reached its destination and its crew has disembarked, the ferry shrinks
    back into the foliage from which it was summoned.

    Sorcerers with an Essence pool may use the following powers while this
    spell is active:

    \subsubsection{Barque of Durant Heartwood} (10m, 1wp; Simple; One day):
    The ship's hull hardens to thick bark, gaining
    \Pool{\StatVal{Essence} / 2}[rounded up] \Modifier-{0} Hull levels. Once
    they fade away, damage marked in them rolls over into regular Hull levels.

    \subsubsection{Hay-Fever Seabloom} (5m; Supplemental; Instant; Pilot):
    Thick, sticky pollen trails in the Floral Ferry's wake. Success on an
    interval of a naval pursuit while fleeing a ship imposes a penalty of
    \Pool{\Val{sorcerer's \StatVal{Intelligence}}} on the pursuing captains'
    next interval.

    \subsubsection{Whirling Maple-Seed Swiftness} (10m, 1wp; Simple; One day;
    Pilot): As long as the sorcerer helms the Floral Ferry, its total Speed is
    doubled.

    \begin{Unavailable}
        A sorcerer with this as her control spell may awaken Evocations from
        the Floral Ferry.
    \end{Unavailable}

    \textit{Distortion} (Goal Number:~5): Distorting the Floral Ferry allows
    the opposing sorcerer to name a new destination that it will sail itself
    towards.
\end{Spell}


\begin{Spell}{Keel Cleaves the Clouds}{%
    Cost={25sm, 2wp},
    Duration=One day,
    Reference=\cite*[p.~311]{db}
}{keel-cleaves-the-clouds}
    As fog or clouds touch the seas, the sorcerer speaks honeyed lies to a
    ship, convincing it that it may sail forward upon them. The enchanted
    ship may sail over mist, fog, or other vapors as though they were water,
    and can ascend vertically through such vapors until it's skimming over
    their surface. In sufficiently misty environs, it's even possible for the
    ship to rise high enough to sail on the clouds themselves. However, while
    vapor-borne, the ship cannot benefit from Speed bonuses from oars or
    currents. If this spell ends, or there's no vapor left for the ship to sail
    on, it descends, landing safe and undamaged, albeit potentially landlocked.

    \begin{Unavailable}
        A sorcerer with this as her control spell is constantly surrounded by
        pale mists, though she may disperse them with a thought unless
        otherwise distracted by involved activity, deep concentration, or
        tumultuous emotion. She may walk on mist or fot as though it were solid
        ground, albeit as difficult terrain~\parencite*[p.~199]{ex3}.
    \end{Unavailable}

    \textit{Distortion} (Goal Number:~8): Distorting this spell causes mist to
    envelop the ship in a thick cloud, making it all but impossible for its
    crew to see outward. Sail rolls to pilot it suffer a \Modifier{-3} penalty,
    and those aboard have no warning if it's about to run out of mist that can
    support it.
\end{Spell}

