\mychapter{background}{Background}

Sagacious Hand is a tall, thin man, with bright green eyes and well-kept hair
and beard, black with gray creeping in around the edges. He is fourty-two years
old, though he has the lines and gray of an older man, and the bearing and
energy of a younger man. He is quick to laugh and eager to listen and learn,
and just as eager to share his skills and understanding.


\mysection{anima-banner}{Anima Banner}

As Sagacious Hand's anima flares, he is surrounded by the colors of twlight:
gold, red, blue, purple, all twinkling like a million fireflies. As his anima
becomes a bonfire, the motes of color explode into glowing script, passages of
lore and forgotten truths, written in beaufitul Old Realm caligraphy, twisting
and swirling, each phrase flaring and then fading to be replaced by some other
text.


\mysection{mortal-life}{Mortal Life}

Sagacious Hand was born Isidro, in a western principality of the Hundred
Kingdoms, into a well-to-do family. His father was a merchant. Isidro was the
oldest of three brothers and two sisters. It was clear from a young age that
Isidro was bright. He excelled in his studies and read voraciously.

Rather than take on the family business, Isidro took his share of the family
inheritance and headed west toward the Scavenger Lands, sure that he was
destined for a greater life than that of a merchant. He studied medicine in
Great Forks and the surrounding areas, always impressing his teachers with his
quick learning and deep understanding. He found patrons, at first in Great
Forks and later in Nexus, wealthy mortals who were more than happy to have a
bright and talented medician in their debt. He was welcomed as an honored guest
in courts and estates, living with the families he treated.

Throughout his travels, Isidro would offer his medical assistance to anyone who
asked. He would often stay in small towns and villages on the road, offering
treatment and healing.

As word of his ability spread, he received letters requesting his presence from
all over the region, as far south as Jiara, and even back in the Hundred
Kingdoms. Isidro accumulated enough wealth for a comfortable retirement, when
the day should finally come.


\mysection{second-breath}{Second Breath}

Isidro received a plea for aide from Vidigueira, a remote trading village on
the Yellow River, east of Great Forks. The village had seemingly been cursed
with an unknown and mysterious disease, which none of the local priests or
healers could cure. He set out at once.

Upon arriving in Vidigueira, Isidro found that nearly the entire town was
infected with some sort of plague. He to work at once attempting to identify
the disease, or to discern some form of treatment, but after days of work he
was no closer to a cure. Worse still, he became infected himself. Isidro only
redoubled his efforts, working night and day, sleeping only when he passed out
at his desk from exhaustion.

After a week, the situation seemed hopeless. Isidro dragged himself from
patient to paient, noting vital signs and changing towels and dressings. His
own fever was becoming dangerous.

That night, while taking the pulse of a bed-ridden man, Isidro's vision began
to fade and his legs gave out under him. He was sure this was the end. But
then, as he drew his final breaths, he felt a warmth, like a beam of strong
sunlight on his face. And he felt better. Amazing, and strong. He stood up and
looked down at the man in the bed, illuminated by the aura of light now
surrounding Isidro. It was as though everything he had ever learned about
philosophy and medicine finally clicked, an understanding that he never even
knew he was lacking. He could practically see the life and Essence flowing
through the man in front of him, and intuitively recognized where it was
blocked or weak.

Isidro bounded out of the house and back to his makeshift laboratory, lighting
up the night with his flaring anima. He laughed, giddy with understanding and
enlightenment, and set about mixing herbs and drawing diagrams of bodies with
lines connecting Essence points, chakras, and organs.

He worked through the night, visiting each patient, and through a combination
of medical herbs, massaging of pressure points, and rebalancing of humors and
Essence, he cured every person living in the town by sunrise.

The people of Vidigueira were, of course, overjoyed. Isidro was hugged and
praised, sobbed on and sung to. He himself was in a daze, more alive than ever,
but also completely exhausted from days of little-to-no sleep. His anima still
glowed, but that seemed only to increase their excitement and wonder. The
town's priest told everyone the stories he'd heard of ancient heros who blazed
with fire and performed miracles. As the town organized a feast and carried
Isidro through the streets, his exhaustion finally overtook him and he drifted
off to sleep.


\mysection{the-dream}{The Dream}

As Isidro slept, he drempt of another time and another life. He half-remembered
friends, and caught glimpses of a long-forgotten lover. He watched memories of
gazing at the moon reflected in an unknown sea. Of a mountain that glowed with
gold and sunlight. Of walking through marble halls into a beautiful library.
For the first time two decades, he felt at home. The woman in his arms was
speaking to him. He looked down as she said his name, ``Sagacious Hand.'' And
then he woke with a start.

As he sat up in the darkness, he was left with a phrase, \emph{The Path of
Balancing Light}, and a vision of a mountain that he knew was to the southwest.
And he knew that was where he, Sagacious Hand, needed to be.


\mysection{the-path}{The Path of Balancing Light}

The Path of Balancing Light is a First Age philosophy, founded by Sagacious
Hand's previous incarnation. It is an attempt to understand the nature and
behavior of Essence, both in individuals and at large. The Sage spent nearly a
century developing it, along with his co-founders, a Lunar, a Sidereal, another
Solar, and a Terrestrial. Together, they founded The Academy of the Path of
Balancing Light, a center of learning and of research.

The Path can be understood through many lenses. Sagacious Hand understands it,
and first conceived of it, through the medical arts. He studied how Essence
moves through a person, affecting their health and their demeanor. His Lunar
mate understood it through her crafting, manipulating Essence through Artifacts
and Geomancy. The Sidereal understood it through martial arts. The other Solar,
an Eclipse, through sorcery. And the Terrestrial, a Fire aspect, through
performance, particularly dance and vocal. They all studied the same Path, much
as the blind men studied the same elephant.

Just as creation has five Elemental Poles, The Path conceives of a person as
having the same five Poles: the Pole of Air is located at the top of the head;
the Pole of Earth in the chest, level with the heart; the Pole of Fire in the
groin; the Pole of Water in the right-hand wrist; and the Pole of Wood in the
left-hand wrist. The balance of these five Poles influences and is influenced
by the flow of Essence within the person.

The Path explains that Essence comprises the energies of these five Poles, just
as light is comprises the colors of the rainbow. As Essence enters a body, like
a prism separates light, the Essence is separated and flows between the Poles.
What most people would understand as Essence is, according to The Path, more
like white light, a mix of many different ``freqencies'' of Essence. Further,
each Essence-user has a distinct spectral Essence signature, influenced by her
Exaltation as well as the balance of her bodily Poles.


\printbibliography[title=References]

% vim: filetype=tex: textwidth=79:

