\mychapter{artifacts}{Artifacts and Other Merits}

\Merit{Mångata}{
    Description={Moonsilver Light Armor},
    Keywords=Silent,
    Rating=Artifact~\Dots{3}
}{mangata}

These flowing robes are woven from incredibly fine strands of moonsilver and
jade. The resulting material has the texture of silk, the strength of steel,
and the glittering opalescence of moonlight on water. There is a single
hearthstone socket in the clasp.

During the First Age, years before the founding of The Academy of the Path of
Balancing Light, when Sagacious Hand and [Lunar Mate] were first developing
feelings for each other, they spent several months working together in the
Northwest. There was a word in one of the local languages, \textit{mångata},
(pronounced \textit{``mo-an-ga-ta''}) which roughtly translated to ``the
glimmering, road-like reflection that the moon creates on water.'' [Lunar Mate]
and Sagacious Hand passed many a long night together, gazing out at
\textit{mångata} on the western sea. The word and all its imagery resonated
with [Lunar Mate], both because of her Lunar nature, and on a more personal
level. She resolved to capture the concept through craft. The result was this
armor, which she gave to Sagacious Hand as a gift on their wedding day.

After the Usurpation, Mångata somehow found its way back into The Academy,
where the robes have rested untouched for an age.

\mysubsection{mangata-evocations}{Evocations of Mångata}

When attuned and worn, \tldr{treat the wearer's Appearance as
\Pool{\Val{Essence}} dots higher for the purpose of computing bonus dice to
instill and persuasion attempts.} This effect cannot raise her Appearance above
five dots.

Mångata is designed to be worn by a Celestial Exalt. Any Exalt may attune to
this artifact and gain the benefit described above, but a non-Celestial Exalt
is unable to unlock any of its Evocations.

% \Charm{Calm Beneath the Waves}{
%     Cost=3m,
%     Duration=One tick,
%     Keywords={Perilous, Withering-only},
%     Mins=Essence 1,
%     Type=Reflexive
% }{mangata-calm-beneath-the-waves}
% 
% As her attacker's sword swings down, the Exalt braces, and her Essence flows
% through her robes to soften and redirect the blow. Strong yet flexible, the
% flowing fabric distributes the force of the attack around its wearer. After a
% \Keyword{withering} attack hits her, but before damage is rolled, she may use
% this Evocation to increase her soak by \Pool{\Val{Essence}}. If the attack does
% not crash the wearer, her attacker loses one point of initiative. This
% Evocation cannot be activated if the wearer is in initiative crash.

\Charm{Allure of Moonlit Waters}{
    Cost=5m,
    Duration=One scene,
    Keywords={Mute, Psyche},
    Mins=Essence 1,
    Type=Simple
}{moangata-allure-of-moonlit-waters}

Just as the moon reflects the power of the sun, Mångata reflects the power of
its Exalted wearer. The wearer suffuses the robes with her Essence, causing
subtle patterns of shape and color to play across the surface, always just out
of the corner of viewers' eyes. The patterns have a fascinating and hypnotic
effect. \tldr{This effect grants the wearer a pool of \Pool{\Val{Appearance}
\times \Val{Essence}} non-Charm bonus dice to use on social actions for the
scene.}

No more than \Pool{\Val{Essence}} bonus dice may be applied to any one action.
Bonus dice may only be spent on actions that are not \emph{overtly} hostile.
For example, they could enhance an action to calm an angry mob, or to talk
someone into a one-sided deal. They could \emph{not} enhance an action to
imtimidate or to threaten.

If the Exalt's anima is glowing or greater, treat her Essence as being one
level higher for the purpose of this Evocation. If her anima level raises after
activating this Evocation, any bonus dice are retroactively added to her pool.


\Merit{Academy of the Path of Balancing Light}{
    Description={Standard Solar Manse},
    Rating=Demesne~\Dots{2}
}{academy}

In the First Age, Sagacious Hand and [Solar Friend] spent a decade scouring
Creation for the perfect place to build The Academy. Finally, they found the
spot: an ancient volcano in the East. The last eruption had blasted the peak
off, forming a caldera with a high southern wall, roughly a quarter mile in
diameter. Exposed gold had combined with flowing lava and unrelenting sunlight,
forming veins of natural orichalcum in the very ground. The entire caldera
pulsed with power and potential.

With the help of [Lunar Mate] and [Sidereal Friend], the group constructed The
Academy in the caldera. The main structure is built from imported marble
infused with orichalcum, accented with orichaucum-flecked obsidian carved from
the floor of the crater.

A visitor to The Academy of the Path of Balancing Light must first scale the
mountain it is built on. The climb is challenging but not deadly. In the First
Age there were paths built to assist, but they have long since fallen away or
been overgrown. No matter the surrounding weather, the summit of the mountain
is surrounded by clouds, and the winds behave strangely. As the visitor reaches
the summit, he finds a path carved into the stone, leading to the Manse proper.

The Academy takes up most of the caldera. Its outer walls are built into the
slope, and rise up thirty feet, white and gold, with enormous honey-gold wooden
double doors, carved with elaborate designs. The grounds within contain
open-air teaching spaces toward the front, a central structure housing a
library, workshop, and hearthstone room, and living space along the back wall.
There are kitchens in the basement, simple rooms (by First-Age standards)
for teachers and important guests, and simple dormitory-style housing on higher
stories, built against the back wall of the caldera.

\mysubsection{academy-effects}{Effects of The Academy}

As an Exalt attunes to The Academy, so too the Manse attunes to the Exalt. The
Academy inspects the Exalt's soul and picks one of her Defining Intimacies to
make its own. The Academy will attempt to pick the Intimacy closest to the
Exalt's heart. If the owner becomes unattuned from The Academy and later
reattunes, it will choose the same Intimacy unless that Intimacy is no longer
Defining, or she has gained a new Defining Intimacy.

As long as the Exalt remains the owner of The Academy, any teaching that
happens in its marble halls will implicitly pass on that Intimacy. A student
listening to a lecture will find the words and ideas connecting in ways the
teacher never consciously intended.

\paragraph{Potential Mechanics:} At the end of any lesson, the Academy makes an
instill action to place its Intimacy as a Minor Intimacy in the heart of the
student, using the teacher's \Pool{\Val{Manipulation} + \Val{Performance}},
plus any of the teacher's relevant specialties. If the lesson was explicitly in
line with The Academy's Intimacy, it adds one success to this roll. The teacher
may not enhance this action with charms, as it the Manse itself channeling the
beliefs of its owner.


\Merit{Hearthstone}{
    Description={Standard Solar Hearthstone},
    Keywords=Linked,
    Rating=Hearthstone~\Dots{2}
}{hearthstone}

The hearthstone produced by The Academy is a round black stone with large
flecks of gold, not unlike the orichalcum-infused obsidian that formed
naturally in its home demesne. In sunlight, the black is shown to be
translucent, containing deep reds, oranges, and purples. The stone feels warm
to the touch.


\Merit{Cult in Vidigueira}{
    Rating=Cult~\Dots{1}
}{cult}

No one will soon forget how ``The Savior of Vidigueira'' delivered them from
certain death (though they may be sketchy on the details). They have since
erected a statue of Sagacious Hand in the town square and declared a holiday in
rememberance, beginning with a night of fasting, followed by feasting and
celebration starting at sunrise. Many whisper prayers for health and healing as
they pass the statue, and stories of the wandering healer have only grown
taller.


\Merit{Disciples of the Path}{
    Rating=Followers~\Dots{1}
}{disciples}

Starting in Vidigueira, Sagacious Hand has been attracting followers. He
currently has twelve, six men and six women. They range in age from thirty to
sixty. All were healed from near-death by Sagacious Hand on his path to The
Academy, and all feel they owe The Teacher their lives. Roughly half the
disciples travel with Sagacious Hand at any given time, the rest off delivering
missives or attending to The Teacher's business in cities.

The Sage has been training his disciples in The Path, as best he has been able
to reconstruct it, as well as in the medical arts. Each has one dot of Lore
(Path of Balancing Light), one or two dots of Medicine, and one or two dots
from their profession.


\printbibliography[title=References]

% vim: filetype=tex: textwidth=79:

