\mychapter{charms}{Charms}

\mysection{excellencies}{Excellencies}

\begin{Charm}{Solar Excellency}{
    Cost=1m/die,
    Duration=Instant,
    Mins={Ability 1, Essence 1},
    Type=Reflexive or Supplemental,
    %Reference=\cite*[p.~255]{ex3}
    Reference={\cite{ex3}}
}{excellency}
    The Solar Exalted may use their Excellencies to enhance any rolled action,
    or any application of a static value. \tldr{To enhance a rolled action, the
    Solar simply spends one mote of Essence per die added to the roll}. The
    Solar may spend up to $(\text{Attribute} + \text{Ability})$ motes, subject
    to the normal limitations on adding dice to a roll with magic (p251).
    \tldr{When using an Excellency to enhance a static value, the Solar spends
    two motes of Essence for every point by which she raises the static value,}
    and may spend up to $(\text{Attribute} + \text{[Ability that contributes to
    the static value]})$ motes, again, subject to normal static value-raising
    limitations. All Excellency use is of instant duration. If the Excellency
    is being used to enhance a dice roll it is considered supplemental. If it
    is being used in a defense it is considered reflexive.
\end{Charm}



\mysection{awareness-charms}{Awareness Charms}

\begin{Charm}{Sensory Acuity Prana}{
    Cost=5m,
    Duration=One scene,
    Mins={Awareness 2, Essence 1},
    Type=Reflexive,
    Reference=Ex 3 p267
}{sensory-acuity-prana}
    A breath of Essence seals the five senses into a more perfect form. The
    Solar’s senses are heightened and attuned to minute motions and sounds, dim
    and noisy conditions. She can differentiate between subtle tastes and
    textures with only the slightest variation. Thus sharpened, it is more
    difficult for characters to escape her notice, or to deceive her hunting
    senses. \tldr{For the rest of the scene, the Exalt’s Awareness rolls
    benefit from double 9s.} If the effect of any Unsurpassed (Sense)
    Discipline applies, reroll 6s until they cease to appear. Use of Sensory
    Acuity Prana comes without the danger of sensory overload; the Charm helps
    the Solar manage her senses more effectively.
\end{Charm}

\begin{Charm}{Surprise Anticipation Method}{
    Cost=\NoCost,
    Duration=Instant,
    Mins={Awareness 3, Essence 1},
    Type=Reflexive,
    Reference=Ex 3 p267
}{surprise-anticipation-method}
    Upon learning this technique, the Solar’s senses guard her from threats she
    is not consciously aware of. Whenever the Solar is in danger—even if she is
    not consciously aware of the threat—her relevant senses will home in on the
    source of danger, enhancing her Awareness to make the threat known to her.
    Surprise Anticipation Method has two functions. First: \tldr{for every 9
    she rolls on an Awareness check to reveal a hidden enemy, trap, or any
    source of harm not readily apparent, she gains a single mote of Essence,
    and for every 10 she gains two.} This charge of Essence can only be used to
    offset the cost of activating Awareness Charms to reveal a threat. Motes
    returned in this fashion may retroactively lower the cost committed to
    Awareness Charms of a scene or longer duration, both lowering the committed
    cost and returning the discounted mote(s) to the Solar’s mote pool. Second:
    \tldr{her senses function even when she is asleep or Incapacitated,
    allowing her to use any of her Awareness Charms subconsciously.} A threat
    revealed to the Solar while she is asleep or unconscious automatically
    revives her, allowing her to defend herself.
\end{Charm}



\mysection{dodge-charms}{Dodge Charms}

\begin{Charm}{Reed in the Wind}{
    Cost=2i/+1Ev,
    Duration=Instant,
    Mins={Dodge 3, Essence 1},
    Type=Reflexive,
    Reference=Ex 3 p299
}{reed-in-the-wind}
    The Exalt draws upon her own momentum to bend and flow with opposing
    forces. \tldr{For every two Initiative spent in response to an attack, the
    player may raise the Exalt’s Evasion by one. Reed in the Wind raises the
    cap on how much the Solar can enhance her Evasion by her Essence.} At Dodge
    5+, Essence 3+, a successful dodge with Reed in the Wind restores one mote.
    This bonus may only occur once per round.
\end{Charm}



\mysection{lore-charms}{Lore Charms}

\begin{Charm}{Harmonious Academic Method}{
    Cost=\NoCost,
    Duration=Permanent,
    Mins={Lore 3, Essence 1},
    Type=Permanent,
    Reference=Ex 3 p330
}{harmonious-academic-method}
    The Solar’s mind covers a spectrum of mastered topics. \tldr{With this
    Charm, add the Solar’s Essence in non-Charm automatic successes to any Lore
    roll that involves a Lore specialty.} In addition, the player may add an
    additional Lore specialty to her list of Lore topics at the end of each
    story. The Storyteller may veto any particular topic, in which case the
    player is allowed to choose another specialty that’s more acceptable.
    Finally, at any point in which the Solar succeeds at a moderately or
    extremely difficult roll to introduce or challenge a fact (p. 237), the
    player may request to add a related topic to the Solar’s library of known
    topics. As with all other topics, this is allowable only at the
    Storyteller’s discretion.
\end{Charm}

\begin{Charm}{First Knowledge's Grace}{
    Cost=4m,
    Duration=One scene,
    Mins={Lore 3, Essence 1},
    Type=Reflexive,
    Reference=Ex 3 p330
}{first-knowledges-grace}
    Affecting a calm and patient demeanor, the Solar is able to project the
    light of her knowledge into the darkest of places. While affecting this
    Charm, the Solar ignores all penalties to teach someone. She can educate a
    person who is deemed medically incapable of learning, such as someone who
    is developmentally disabled, or someone who has suffered traumatic injury
    or privation by the Fair Folk. This Charm does not affect social influence
    rolls to persuade a character of something.
\end{Charm}

\begin{Charm}{Flowing Mind Prana}{
    Cost=1xp+,
    Duration=Instant,
    Mins={Lore 5, Essence 1},
    Type=Simple,
    Reference=Ex 3 p331
}{flowing-mind-prana}
    The Lawgiver is a master instructor, capable of passing on truths and
    talents as surely as the sun passes daylight. \tldr{To activate this Charm,
    the Solar commits a number of experience points from her own unspent
    experience total. She may confer these experience points to another
    character by delivering a lesson she has constructed, allowing her to train
    a character’s Attributes or Abilities} up to a rating of 5, even if this
    puts the character beyond her own rating. \tldr{However, for each three
    experience points the Solar spends on the character in question, that
    character must adopt, at the Minor level, an Intimacy the Solar holds.} The
    Solar may choose which Intimacy is conferred. For each three experience
    points conferred, the Solar may confer individual Intimacies, or she may
    increase a single Intimacy’s intensity from Minor to Major, or from Major
    to Defining, so long as she holds that Intimacy at the Major or Defining
    level herself. Intimacies conferred in this manner cannot be decayed for
    any reason until the character has performed at least one task equal to
    that Intimacy’s intensity (p. 215).

    The Solar has sole discretion over who is able to benefit from the
    experience points on offer. Refer to training times on page 178 to
    determine how long each training session should take. \tldr{At the end of
    each story, the Solar may roll a number of dice equal to experience points
    spent on this Charm, regaining a number of experience equal to her
    successes, but not beyond the total amount of experience she expended in
    training.} A Solar with Socialize Charms related to the creation of
    personas may use this Charm while in the guise of a persona, but she must
    pay from both her main unspent experience total and the persona’s unspent
    experience total to do so. Lastly, the Solar cannot benefit from this or
    any other experience-granting training Charm in the same story in which she
    uses it to benefit someone else.
\end{Charm}



\mysection{medicine-charm}{Medicine Charms}

\begin{Charm}{Ailment-Rectifying Method}{
    Cost=3m,
    Duration=Instant,
    Mins={Medicine 1, Essence 1},
    Type=Simple,
    Reference=Ex 3 p341
}{ailment-rectifying-method}
    Disease  and  pestilence  cannot  stand  against  the  Solar Exalted. This
    Charm represents an hour spent treating a patient for an illness the Exalt
    has properly diagnosed. \tldr{Roll the Exalt’s $(\text{Intelligence} +
    \text{Medicine})$ against the disease’s morbidity (p. 233) and add half the
    extra successes to the patient’s Resistance roll at the next interval.}
    Through this Charm, the Solar can weaken or even cure supernatural maladies
    such as the Great Contagion. However, the target must remain in bed, and
    must be bathed, fed, and otherwise given care for the duration of the next
    interval. These ministrations can be performed by the Solar’s assistants.
    The Exalt may use this Charm to treat her own diseases, though some may
    require a stunt or special instruments to treat.
\end{Charm}

\begin{Charm}{Plague-Banishing Incitation}{
    Cost=2m 1wp,
    Duration=Instant,
    Mins={Medicine 3, Essence 1},
    Type=Reflexive,
    Prerequisites=\nameref{charm:ailment-rectifying-method},
    Reference=Ex 3 p341
}{plague-banishing-incitation}
    \tldr{If the Lawgiver generates at least double her patient’s Stamina or
    Resistance (whichever is greater) in successes through the use of the
    prerequisite}, she may use this Charm to demand that a malaise leave her
    patient’s body. \tldr{This causes the disease’s interval to conclude
    immediately, and allows the patient the benefit of all rather than half the
    Solar’s extra successes from Ailment-Rectifying Method.} If successful, the
    pestilence immediately vacates the host, and the patient begins to recover
    over the course of a day. \tldr{If the Solar saves a character from death’s
    doorstep through the use of this Charm, she gains one point of temporary
    Willpower.}
\end{Charm}

\begin{Charm}{Wound-Mending Care Technique}{
    Cost=5m 1wp,
    Duration=Instant,
    Mins={Medicine 3, Essence 1},
    Type=Simple,
    Reference=Ex 3 p342
}{wound-mending-care-technique}
    Through mastery of Essence flows and a keen understanding of the body, the
    Solar can repair even the most ruinous damage at an incredible pace. The
    Solar spends fifteen minutes to an hour doctoring the patient, depending on
    the severity of the wounds. She still requires the normal medicines,
    bandages, and any tools that might be needed for more complex operations,
    but her results are nonetheless miraculous. \tldr{Roll
    $(\text{Intelligence} + \text{Medicine})$ with double 9s at the end of the
    treatment. This is the number of bashing or lethal health levels that will
    be restored} if the patient remains in bed for the rest of the day. In
    addition, \tldr{if the Solar’s treatment would raise her patient two or
    more wound levels, she gains a point of Willpower.}
\end{Charm}

% vim: filetype=tex: textwidth=79:

