\mychapter{artifacts}{Artifacts and Other Merits}

\begin{Merit}{Mångata}{
    Description={Moonsilver Light Armor, Artifact~\Dots{3}},
    Keywords=Silent
}{mangata}
These flowing robes are woven from incredibly fine strands of moonsilver and
jade. The resulting material has the texture of silk, the strength of steel,
and the glittering opalescence of moonlight on water. There is a single
hearthstone socket in the clasp.

During the First Age, years before the founding of The Academy of the Path of
Balancing Light, when Sagacious Hand and [Lunar Mate] were first developing
feelings for each other, they spent several months working together in the
Northwest. There was a word in one of the local languages, \textit{mångata},
(pronounced \textit{``mo-an-ga-ta''}) which roughtly translated to ``the
glimmering, road-like reflection that the moon creates on water.'' [Lunar Mate]
and Sagacious Hand passed many a long night together, gazing out at
\textit{mångata} on the western sea. The word and all its imagery resonated
with [Lunar Mate], both because of her Lunar nature, and on a more personal
level. She resolved to capture the concept through craft. The result was this
armor, which she gave to Sagacious Hand as a gift on their wedding day.

\mysubsection{mangata-evocations}{Evocations of Mångata}

When attuned and worn, treat the wearer's Appearance as $(\mathrm{Essence})$
dots higher for the purpose of computing bonus dice to instill and persuasion
attempts. This effect cannot raise her Appearance above five dots.

Mångata is designed to be worn by a Celestial Exalt. Any Exalt may attune to
this artifact and gain the benefit described above, but a non-Celestial Exalt
is unable to unlock any of its evocations.

\begin{Charm}{Calm Beneath the Waves}{
    Cost=3m,
    Duration=One tick,
    Keywords={Perilous, Withering-only},
    Mins=Essence 1,
    Type=Reflexive
}{mangata-evocation-calm}
As her attacker's sword swings down, the Exalt braces, and her essence flows
through her robes to soften and redirect the blow. Strong yet flexible, the
flowing fabric distributes the force of the attack around its wearer. After a
\textbf{withering} attack hits her, but before damage is rolled, she may use
this evocation to increase her soak by $(\mathrm{Essence})$. If the attack does
not crash the wearer, her attacker loses one point of initiative. This
evocation cannot be activated if the wearer is in initiative crash.
\end{Charm}

\begin{Charm}{Evocation 2}{
    Cost=5m,
    Duration=One scene,
    Keywords={Mute, Psyche},
    Mins=Essence 2,
    Type=Simple
}{mangata-evocation-2}
Just as the moon reflects the power of the sun, Mångata reflects the power of
its Exalted wearer. The wearer suffuses the robes with her essence, causing
subtle patterns of shape and color to play across the surface, always just out
of the corner of viewers' eyes. The patterns have a fascinating and hypnotic
effect. This effect grants the wearer a pool of $(\mathrm{Appearance} \times
\mathrm{Essence})$ non-charm bonus dice to use on social actions for the scene.
If the Exalt's anima is glowing or greater, this pool increases to
$(\mathrm{Appearance} \times [\mathrm{Essence} + 1])$. If her anima level
raises after activating this evocation, the bonus dice are retroactively added
to her pool.

No more than $(\mathrm{Essence})$ bonus dice may be applied to any one action,
or no more than $(\mathrm{Essence} + 1)$ if the Exalt's anima is glowing or
greater. Bonus dice may only be spent on actions that are not \emph{overtly}
hostile. For example, they could enhance an action to calm an angry mob, or to
talk someone into a one-sided deal. They could \emph{not} enhance an action to
imtimidate or to threaten.
\end{Charm}
\end{Merit}

\begin{Merit}{Academy of the Path of Balancing Light}{
    Description=Standard Solar Manse
}{academy}
In the First Age, [Solar Friend] and Sagacious Hand spent years scouring
Creation for the perfect place to build The Academy. Finally, [Solar Friend]
found the spot: an ancient and long-dormant volcano in the East, where exposed
gold had combined with flowing lava and unrelenting sunlight, forming veins of
natural Orachalcum in the very ground. The entire caldera pulsed with power and
potential.

With the help of [Lunar Mate] and [Sidereal Friend], the group constructed the
Academy at the center of the caldera. The main structure is built from imported
marble infused with Orachalcum, accented with Orachaucum-flecked obsidian
carved from the caldera.

A visitor to The Academy must first scale the mountain it is built on. The
climb is challenging but not deadly. In the First Age there were paths built to
assist, but they have long since fallen away or been overgrown. No matter the
surrounding weather, the summit of the mountain is surrounded by clouds, and
the winds behave strangely.

The Academy takes up most of the caldera, its outer walls built into the sides
of the bowl.

\mysubsection{academy-effects}{Effects of The Academy}

As an Exalt attunes to The Academy, so too the Manse attunes to the Exalt. The
Academy inspects the Exalt's soul and picks one of her Defining Intimacies to
make its own. The Academy will attempt to pick the Intimacy closest to the
Exalt's heart. If the owner becomes unattuned from The Academy and later
reattunes, it will choose the same Intimacy unless that Intimacy is no longer
Defining, or she has gained a new Defining Intimacy.

As long as the Exalt remains the owner of The Academy, any teaching that
happens in its marble halls will implicitly pass on that Intimacy. A student
listening to a lecture will find the words and ideas connecting in ways the
teacher never consciously intended. Mechanically, at the end of any lesson, the
Academy makes an instill action to place its Intimacy as a Minor Intimacy in
the heart of the student, using the teacher's $(\mathrm{Manipulation} +
\mathrm{Performance})$, plus any of the teacher's relevant specialties. If the
lesson was explicitly in line with The Academy's Intimacy, it adds one success
to this roll. The teacher may not enhance this action with charms, as it the
Manse itself channeling the beliefs of its owner.
\end{Merit}

\begin{Merit}{Hearthstone}{
    Description=Standard Solar Hearthstone,
    Keywords=Linked
}{hearthstone}
The hearthstone produced by The Academy is a round black stone with large
flecks of gold. In sunlight, the black is becomes slightly translucent, giving
way to deep reds, oranges, and purples. The stone feels warm to the touch.

When an Exalt is attuned to The Academy, in a two mile radius around the
hearthstone, people who would be sympathetic to The Academy's Intimacy feel
drawn to the location of the stone. They do not know particularly why, only
that there's something important there.
\end{Merit}

% vim: filetype=tex: textwidth=79:

