\mychapter{charms}{Charms}

% \ChapterContents

\CharmSection{excellencies}{Excellencies}

\Charm{Solar Excellency}{
    Cost=1m per die,
    Duration=Instant,
    Mins={Ability 1, Essence 1},
    Type=Reflexive or Supplemental,
    Reference=\cite*[p.~255]{ex3}
}{excellency}

The Solar Exalted may use their Excellencies to enhance any rolled action, or
any application of a static value. \tldr{To enhance a rolled action, the Solar
simply spends one mote of Essence per die added to the roll}. The Solar may
spend up to \Pool{\Val{Attribute} + \Val{Ability}} motes, subject to the normal
limitations on adding dice to a roll with magic \parencite*[p.~251]{ex3}
\tldr{When using an Excellency to enhance a static value, the Solar spends two
motes of Essence for every point by which she raises the static value,} and may
spend up to \Pool{\Val{Attribute} + \Val{[Ability that contributes to the
static value]}} motes, again, subject to normal static value-raising
limitations. All Excellency use is of instant duration. If the Excellency is
being used to enhance a dice roll it is considered supplemental. If it is being
used in a defense it is considered reflexive.



\CharmSection{awareness-charms}{Awareness Charms}

\Charm{Sensory Acuity Prana}{
    Cost=5m,
    Duration=One scene,
    Mins={Awareness 2, Essence 1},
    Type=Reflexive,
    Reference=\cite*[p.~267]{ex3}
}{sensory-acuity-prana}

A breath of Essence seals the five senses into a more perfect form. The Solar's
senses are heightened and attuned to minute motions and sounds, dim and noisy
conditions. She can differentiate between subtle tastes and textures with only
the slightest variation. Thus sharpened, it is more difficult for characters to
escape her notice, or to deceive her hunting senses. \tldr{For the rest of the
scene, the Exalt's Awareness rolls benefit from double 9s.} If the effect of
any Unsurpassed (Sense) Discipline applies, reroll 6s until they cease to
appear. Use of Sensory Acuity Prana comes without the danger of sensory
overload; the Charm helps the Solar manage her senses more effectively.


\Charm{Keen Hearing and Touch Technique}{
    Cost=3m or 6m 1wp,
    Duration=One scene,
    Mins={Awareness 3, Essence 1},
    Type=Simple,
    Prerequisites=\nameref{charm:sensory-acuity-prana},
    Reference=\cite*[p.~269]{ex3}
}{keen-hearing-and-touch-technique}

The Lawgiver listens with the intensity of an owl, and feels movement in the
world like a spider feels a touch against its web. The Exalt may identify
fabrics and minerals she knows with a cursory touch, and can hear at
frequencies several times lower than a human. She can listen clearly to
conversations through thick stone walls, hear creatures burrowing in the
ground, ants marching on the branches above her head, and other, similar feats.
\tldr{For many actions that would require success on a roll at difficulty~2, the
Solar can succeed without a roll. For more difficult actions, the difficulty is
lowered by 1, and the Solar gains one automatic success. If she has a specialty
that can be logically applied to the roll, the difficulty drops to 1.} For
example, a Solar who is unfamiliar with art crime will find it more difficult
to identify a faked painting by touch than a Solar with an Investigation
specialty in detecting forgeries. These benefits do not apply to detecting
opponents in stealth.

This Charm follows the special activation rules of Keen Sight Technique
\parencite*[p.~267]{ex3}.

\paragraph{Special activation rules:} The player may choose to activate Keen
Sight Technique by paying six motes, one willpower. Doing so sets the duration
of this Charm to Indefinite. Despite being Simple type Charms, each Keen
(Sense) Technique can be activated simultaneously by paying the full cost of
each. In addition, these Charms are compatible with Sensory Acuity Prana as
well as with each other.



\CharmSection{dodge-charms}{Dodge Charms}

\Charm{Reed in the Wind}{
    Cost=2i per 1 Evasion,
    Duration=Instant,
    Keywords=Perilous,
    Mins={Dodge 3, Essence 1},
    Type=Reflexive,
    Reference=\cite*[p.~299]{ex3}
}{reed-in-the-wind}

The Exalt draws upon her own momentum to bend and flow with opposing forces.
\tldr{For every two Initiative spent in response to an attack, the player may
raise the Exalt's Evasion by one. Reed in the Wind raises the cap on how much
the Solar can enhance her Evasion by her Essence.} At Dodge 5+, Essence 3+, a
successful dodge with Reed in the Wind restores one mote. This bonus may only
occur once per round.


\Charm{Reflex Sidestep Technique}{
    Cost=5m,
    Duration=Instant,
    Keywords=Uniform,
    Mins={Dodge 3, Essence 1},
    Type=Reflexive,
    Reference=\cite*[p.~299]{ex3}
}{reflex-sidestep-technique}

The Solar's preternatural awareness of her surroundings makes her nearly
impossible to harm. Even when struck unaware, she may part herself from
her foe's attack, undoing the damage that was done to her. \tldr{This Charm may be
activated in response to an ambush attack, a trap, or other damaging effect the
Solar is completely unaware of, setting her Evasion to two against the attack
and adding an additional point of Evasion for every 1 or 2 in the attack}
(before Charms such as Excellent Strike). If the Solar's Evasion recovers to
its full value, she may apply additional Dodge Charms if necessary.



\CharmSection{lore-charms}{Lore Charms}

\Charm{Harmonious Academic Method}{
    Cost=\NoCost,
    Duration=Permanent,
    Mins={Lore 3, Essence 1},
    Type=Permanent,
    Reference=\cite*[p.~330]{ex3}
}{harmonious-academic-method}

The Solar's mind covers a spectrum of mastered topics. \tldr{With this Charm,
add the Solar's Essence in non-Charm automatic successes to any Lore roll that
involves a Lore specialty.} In addition, the player may add an additional Lore
specialty to her list of Lore topics at the end of each story. The Storyteller
may veto any particular topic, in which case the player is allowed to choose
another specialty that's more acceptable. Finally, at any point in which the
Solar succeeds at a moderately or extremely difficult roll to introduce or
challenge a fact \parencite*[p.~237]{ex3}, the player may request to add a
related topic to the Solar's library of known topics. As with all other topics,
this is allowable only at the Storyteller's discretion.


\Charm{First Knowledge's Grace}{
    Cost=4m,
    Duration=One scene,
    Mins={Lore 3, Essence 1},
    Prerequisites=\nameref{charm:harmonious-academic-method},
    Type=Reflexive,
    Reference=\cite*[p.~330]{ex3}
}{first-knowledges-grace}

Affecting a calm and patient demeanor, the Solar is able to project the light
of her knowledge into the darkest of places. While affecting this Charm, the
Solar ignores all penalties to teach someone. She can educate a person who is
deemed medically incapable of learning, such as someone who is developmentally
disabled, or someone who has suffered traumatic injury or privation by the Fair
Folk. This Charm does not affect social influence rolls to persuade a character
of something.


\Charm{Flowing Mind Prana}{
    Cost=1xp+,
    Duration=Instant,
    Mins={Lore 5, Essence 1},
    Prerequisites=\nameref{charm:first-knowledges-grace},
    Type=Simple,
    Reference=\cite*[p.~331]{ex3}
}{flowing-mind-prana}

The Lawgiver is a master instructor, capable of passing on truths and talents
as surely as the sun passes daylight. \tldr{To activate this Charm, the Solar
commits a number of experience points from her own unspent experience total.
She may confer these experience points to another character by delivering a
lesson she has constructed, allowing her to train a character's Attributes or
Abilities} up to a rating of 5, even if this puts the character beyond her own
rating. \tldr{However, for each three experience points the Solar spends on the
character in question, that character must adopt, at the Minor level, an
Intimacy the Solar holds.} The Solar may choose which Intimacy is conferred.
For each three experience points conferred, the Solar may confer individual
Intimacies, or she may increase a single Intimacy's intensity from Minor to
Major, or from Major to Defining, so long as she holds that Intimacy at the
Major or Defining level herself. Intimacies conferred in this manner cannot be
decayed for any reason until the character has performed at least one task
equal to that Intimacy's intensity \parencite*[p.~215]{ex3}.

The Solar has sole discretion over who is able to benefit from the experience
points on offer. Refer to training times on page 178 to determine how long each
training session should take. \tldr{At the end of each story, the Solar may
roll a number of dice equal to experience points spent on this Charm, regaining
a number of experience equal to her successes, but not beyond the total amount
of experience she expended in training.} A Solar with Socialize Charms related
to the creation of personas may use this Charm while in the guise of a persona,
but she must pay from both her main unspent experience total and the persona's
unspent experience total to do so. Lastly, the Solar cannot benefit from this
or any other experience-granting training Charm in the same story in which she
uses it to benefit someone else.


\Charm{Essence-Lending Method}{
    Cost=3m,
    Duration=Instant,
    Mins={Lore 1, Essence 1},
    Type=Simple,
    Reference=\cite*[p.~331]{ex3}
}{essence-lending-method}

The Lawgiver fortifies her allies with actions as surely as with words. Upon
touching a target and paying three motes, \tldr{the Solar may transfer up to
\Pool{\Val{Essence} \times 3} motes from her mote pool to her target's. In
addition, once per scene she may roll \Pool{\Val{Wits} + \Val{Lore}},
generating a number of motes equal to her successes and awarding them to her
target.} If the target cannot accept all the motes transferred by
Essence-Lending Method he has until his next action to spend them before they
dissipate.



\CharmSection{medicine-charm}{Medicine Charms}

\Charm{Ailment-Rectifying Method}{
    Cost=3m,
    Duration=Instant,
    Mins={Medicine 1, Essence 1},
    Type=Simple,
    Reference=\cite*[p.~341]{ex3}
}{ailment-rectifying-method}

Disease  and  pestilence  cannot  stand  against  the  Solar Exalted. This
Charm represents an hour spent treating a patient for an illness the Exalt has
properly diagnosed. \tldr{Roll the Exalt's \Pool{\Val{Intelligence} +
\Val{Medicine}} against the disease's morbidity \parencite*[p.~233]{ex3} and
add half the extra successes to the patient's Resistance roll at the next
interval.} Through this Charm, the Solar can weaken or even cure supernatural
maladies such as the Great Contagion. However, the target must remain in bed,
and must be bathed, fed, and otherwise given care for the duration of the next
interval. These ministrations can be performed by the Solar's assistants. The
Exalt may use this Charm to treat her own diseases, though some may require a
stunt or special instruments to treat.


\Charm{Plague-Banishing Incitation}{
    Cost=2m 1wp,
    Duration=Instant,
    Mins={Medicine 3, Essence 1},
    Type=Reflexive,
    Prerequisites=\nameref{charm:ailment-rectifying-method},
    Reference=\cite*[p.~341]{ex3}
}{plague-banishing-incitation}

\tldr{If the Lawgiver generates at least double her patient's Stamina or
Resistance (whichever is greater) in successes through the use of the
prerequisite}, she may use this Charm to demand that a malaise leave her
patient's body. \tldr{This causes the disease's interval to conclude
immediately, and allows the patient the benefit of all rather than half the
Solar's extra successes from Ailment-Rectifying Method.} If successful, the
pestilence immediately vacates the host, and the patient begins to recover over
the course of a day. \tldr{If the Solar saves a character from death's doorstep
through the use of this Charm, she gains one point of temporary Willpower.}


\Charm{Wound-Mending Care Technique}{
    Cost=5m 1wp,
    Duration=Instant,
    Mins={Medicine 3, Essence 1},
    Type=Simple,
    Reference=\cite*[p.~342]{ex3}
}{wound-mending-care-technique}

Through mastery of Essence flows and a keen understanding of the body, the
Solar can repair even the most ruinous damage at an incredible pace. The Solar
spends fifteen minutes to an hour doctoring the patient, depending on the
severity of the wounds. She still requires the normal medicines, bandages, and
any tools that might be needed for more complex operations, but her results are
nonetheless miraculous. \tldr{Roll \Pool{\Val{Intelligence} + \Val{Medicine}}
with double 9s at the end of the treatment. This is the number of bashing or
lethal health levels that will be restored} if the patient remains in bed for
the rest of the day. In addition, \tldr{if the Solar's treatment would raise
her patient two or more wound levels, she gains a point of Willpower.}


\Charm{Wound-Cleansing Meditation}{
    Cost=10m,
    Duration=Instant,
    Mins={Medicine 3, Essence 1},
    Type=Simple,
    Reference=\cite*[p.~342]{ex3}
}{wound-cleansing-meditation}

The Solar's advanced medical techniques allow her to draw the poison from
unnatural wounds. With this Charm, the Solar spends an hour cleaning and
wrapping wounds, disinfecting and draining injuries and preparing the patient
for more complex internal treatment. At the end of the treatment, \tldr{convert
the patient's aggravated damage to lethal damage.} This allows the Solar to
treat damaged tissue and to attempt to reattach severed limbs with
\nameref{charm:wound-mending-care-technique}. This Charm does not allow the
regrowth of lost tissue.


\Charm{Contageon-Curing Touch}{
    Duration=Permanent,
    Mins={Medicine 4, Essence 2},
    Prerequisites=\nameref{charm:plague-banishing-incitation},
    Type=Permanent,
    Reference=\cite*[p.~342]{ex3}
}{contageon-curing-touch}

The Solar \tldr{permanently gains \Pool{\Val{Essence}} successes to treat forms
of disease,} even if she does not have the proper tools or medicine to do so.
Her efforts still must be efficacious and logical, but even if she lacks the
most ideal instruments, she can still attempt to cure a plague or other
sickness. Once a patient has been treated by the Solar, \tldr{if he recovers,
he gains four automatic non-Charm successes to resist disease virulence for the
rest of the season.}


\Charm{Instant Treatment Methodology}{
    Cost={5m 1wp or 5i 1wp},
    Duration=Instant,
    Mins={Medicine 4, Essence 2},
    Prerequisites=\nameref{charm:wound-cleansing-meditation},
    Type=Reflexive,
    Reference=\cite*[p.~342]{ex3}
}{instant-treatment-methodology}

This Charm allows the Solar to complete up to an hour of medical treatment in a
handful of seconds. \tldr{Using this Charm lowers the treatment time required
for one Simple-type Medicine Charm.} The Solar still requires the proper
medicines and surgical tools, but may eliminate the need for such with a
properly medical stunt, such as tapping her patient's pressure points to
increase the flow of Essence or massaging a person's heart until it starts
beating


\Charm{Master Chirurgeon Meditation}{
    Duration=Permanent,
    Mins={Medicine 5, Essence 4},
    Prerequisites=Any Medicine Charm,
    Type=Permanent,
    Reference=\cite*[p.~345]{ex3}
}{master-chirurgeon-meditation}

The Exalt hones her Essence through her medical knowledge to save lives.
Through practice and meditation, internal vows and moments of celestial focus,
she calibrates her spirit. \tldr{This Charm permanently lowers the cost of the
\hyperref[charm:excellency]{Medicine Excellency} to one mote per two dice.}



\CharmSection{performance-charms}{Performance Charms}

\Charm{Masterful Performance Exercise}{
    Cost=2m,
    Duration=Instant,
    Mins={Performance 3, Essence 1},
    Type=Supplemental,
    Reference=\cite*[p.~361]{ex3}
}{masterful-performance-exercise}

The Solar's talent is not free or instinctual, but rather the hard-won
excellence that comes from a lifetime of practice. This Charm supplements a
Performance-based action, \tldr{granting one automatic success and rerolling 1s
until 1s fail to appear.} This Charm also makes the Exalt's 1s unavailable to
magic that might interfere with her performance.



\CharmSection{resistance-charms}{Resistance Charms}

\Charm{Durability of Oak Meditation}{
    Cost=3m,
    Duration=One tick,
    Keywords=Dual,
    Mins={Resistance 2, Essence 1},
    Type=Reflexive,
    Reference=\cite*[p.~374]{ex3}
}{durability-of-oak-meditation}

A child cannot cleave a tree with a dull knife, nor can a foe hope to strike
down the Solar with his petty blade. \tldr{Against a \Keyword{withering} or
\Keyword{decisive} attack, this Charm reduces raw damage by two. Against a
\Keyword{decisive} attack it also grants the Exalt four hardness.} Note that
the hardness bonus cannot be applied during crash.


\Charm{Spirit Strengthens the Skin}{
    Cost=1m per damage die removed,
    Duration=Instant,
    Keywords=Withering-only,
    Mins={Resistance 2, Essence 1},
    Prerequisites=\nameref{charm:durability-of-oak-meditation},
    Type=Reflexive,
    Reference=\cite*[p.~374]{ex3}
}{spirit-strengthens-the-skin}

The Solar channels Essence through her enduring toughness, hardening her skin
and muscles beyond their mortal limits. \tldr{After an attack hits her, but
before damage is rolled, she may increase her soak at a rate of one mote per
point. She may no more than double her natural soak in this fashion.} This
effect is incompatible with any magic that allows the Exalt to soak a
\Keyword{decisive} attack with withering-only magic.


\Charm{Ox-Body Technique}{
    Duration=Permanent,
    Keywords=Stackable,
    Mins={Resistance 1, Essence 1},
    Type=Permanent,
    Reference=\cite*[p.~375]{ex3}
}{ox-body-technique}

The bodies of the Exalted are much more durable than those of mere mortals. To
help simulate this, an Exalt may buy extra health levels with this Charm. The
purchasing choices are based on the character's Stamina rating:

At Stamina 1 and 2: One -1 and one -2 health level.

\tldr{3 and 4: One -1 and two -2 health levels.}

5: One -0, one -1, and one -2 health level.

The Solar may purchase Ox-Body Technique \Pool{\Val{Resistance}} times. If she
increases her Stamina after purchasing Ox-Body Technique, her health levels
automatically change to reflect the new rating.


\printbibliography[title=References]


\onecolumn
\pagestyle{empty}
\cleardoublepage

\pagestyle{main}
\mysection{charm-summary}{Charm Summary}

\PrintCharmList

% vim: filetype=tex: textwidth=79:

